\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-31 OaklandSubmission/intro.tex
changes in example
example fonts
spelling in intro

 This paper presents such a framework for Secure
 Two-party Computation (\mpc),
%
%Most cryptographic tools rely on circuit as abstractions for any general computation but real-life developers write programs. It is critical to address this fundamental  representation gap to make cryptography accessible to non-crypto specialist developers. In this work, we address this gap for the case of secure multi-party computation.
%
%Most cryptographic tools are very hard to use non-crypto specialist developers. The task becomes even more tedious and error-prone for the case of secure multiparty computation since different protocol implementations require the function to be expressed in different representations such as Boolean or Arithmetic circuits. To make cryptography accessible to non-crypto specialist developers, we need to design systems that do crypto automatically and satisfy the properties of ... 
%
%Secure Two-party Computation (\mpc)~(\cite{yao,gmw}) is
a powerful
cryptographic technique that allows two mutually distrusting parties
to compute a publicly known joint function of their secret inputs in a way that both
the parties learn nothing about the inputs of each other beyond what
is revealed by their (possibly different) outputs. For example, \mpc
can be used for {\em secure
prediction}~(\cite{shafindss,wu,barni,minionn,secureml}),
where one party (the server) holds a proprietary classifier to predict
a label (e.g., a disease, genomics, or spam detection), and the other
party (the client) holds a private input that it wants to run the
classifier on. Using \mpc guarantees that the server learns nothing
about the client's input or output, and that the client learns nothing
about the classifier, beyond what is revelaed by the output
label.

@@

Alternatively, Alice can use a tool such as ABY (Demmlet et
al.~\cite{aby}) that allows
the computation to be expressed as a combination of arithmetic and
boolean circuits. However, here, the programming interface is quite
low-level: the programmer is required to first manually split the
computation into arithmetic and boolean components, and then write the
circuits for all the components manually, including the appropriate
inter-conversion gates between them. Clearly, writing correct
and efficient protocols in such a framework is beyond an average
programmer who does not understand the various trade-offs between
arithmetic and boolean circuits, and even for an expert cryptographer,
writing large computations in such a framework can be tedious and
error-prone (a sentiment echoed by Demmler et al.~\cite{aby} themselves).

@@

\begin{figure}
\begin{lstlisting}[language=C]
uint w[30] = input1(); uint b = input1();
uint x[30] = input2();
uint acc = 0;
for i in [0:30] { acc =  acc + (w[i] * x[i]); }
output2((acc > b) ? 1 : 0) //only to party 2
\end{lstlisting}
\caption{\tool code for $w^Tx >b$}
\label{fig:ex-sml}
\end{figure}

@@

\subsubsection*{Cryptogaphic-cost aware compiler} The \tool compiler
compiles a source program to a hybrid computation consisting
of \emph{public} and \emph{secret} parts. In the example above, for
instance, \tool compiler realizes that the array index~\ls{i} is
public, and generates non-cryptographic code for the array accesses.
Further, within the secret parts, \tool compiler is
aware
of the cryptographic costs of arithmetic and boolean representations
of the source language operators. Based on these costs, the compiler
automatically picks arithmetic or boolean
representations for different sub-parts, and generates the
corresponding circuits along with the required inter-conversion
gates. The outcome is an effcient \mpc protocol combining arithmetic
and boolean circuits, while the programmer remains
oblivious of all these cryptographic details. Indeed, \tool is the
first such cryptographic-cost aware compiler.

>>>>

 This paper presents such a framework for Secure
 Two-party Computation (\mpc),
%
%Most cryptographic tools rely on circuit as abstractions for any general computation but real-life developers write programs. It is critical to address this fundamental  representation gap to make cryptography accessible to non-crypto specialist developers. In this work, we address this gap for the case of secure multi-party computation.
%
%Most cryptographic tools are very hard to use non-crypto specialist developers. The task becomes even more tedious and error-prone for the case of secure multiparty computation since different protocol implementations require the function to be expressed in different representations such as Boolean or Arithmetic circuits. To make cryptography accessible to non-crypto specialist developers, we need to design systems that do crypto automatically and satisfy the properties of ... 
%
%Secure Two-party Computation (\mpc)~(\cite{yao,gmw}) is
a powerful
cryptographic technique that allows two mutually distrusting parties
to compute a publicly known joint function of their secret inputs in a way that both
the parties learn nothing about the inputs of each other beyond what
is revealed by their (possibly different) outputs. For example, \mpc
can be used for {\em secure
prediction}~(\cite{shafindss,wu,barni,minionn,secureml}),
where one party (the server) holds a proprietary classifier to predict
a label (e.g., a disease, genomics, or spam detection), and the other
party (the client) holds a private input that it wants to run the
classifier on. Using \mpc guarantees that the server learns nothing
about the client's input or output, and that the client learns nothing
about the classifier, beyond what is revealed by the output
label.

@@

Alternatively, Alice can use a tool such as ABY (Demmler et
al.~\cite{aby}) that allows
the computation to be expressed as a combination of arithmetic and
boolean circuits. However, here, the programming interface is quite
low-level: the programmer is required to first manually split the
computation into arithmetic and boolean components, and then write the
circuits for all the components manually, including the appropriate
inter-conversion gates between them. Clearly, writing correct
and efficient protocols in such a framework is beyond an average
programmer who does not understand the various trade-offs between
arithmetic and boolean circuits, and even for an expert cryptographer,
writing large computations in such a framework can be tedious and
error-prone (a sentiment echoed by Demmler et al.~\cite{aby} themselves).

@@

\begin{figure}
\begin{lstlisting}[language=C,mathescape=true]
$\mathtt{
uint\;w[30] = input1();\;\;uint\;b = input1();
}$
$\mathtt{
uint\;x[30] = input2();
}$
$\mathtt{
uint\;acc = 0;
}$
$\mathtt{
for\;i\;in\;[0:30]\;\{\;acc\;=\;acc\;+\;(w[i]\;\times\;x[i]);\;\}
}$
$\mathtt{
output2((acc > b)\;?\;1\;:\;0)\;\text{{\color{red}//only to party 2}}
}$
\end{lstlisting}
\caption{\tool code for $w^Tx >b$}
\label{fig:ex-sml}
\end{figure}

@@

\subsubsection*{Cryptographic-cost aware compiler} The \tool compiler
compiles a source program to a hybrid computation consisting
of \emph{public} and \emph{secret} parts. In the example above, for
instance, \tool compiler realizes that the array index~\ls{i} is
public, and generates non-cryptographic code for the array accesses.
Further, within the secret parts, \tool compiler is
aware
of the cryptographic costs of arithmetic and boolean representations
of the source language operators. Based on these costs, the compiler
automatically picks arithmetic or boolean
representations for different sub-parts, and generates the
corresponding circuits along with the required inter-conversion
gates. The outcome is an efficient \mpc protocol combining arithmetic
and boolean circuits, while the programmer remains
oblivious of all these cryptographic details. Indeed, \tool is the
first such cryptographic-cost aware compiler.
